Efficient pedigree recording for fast population genetics simulation

### 2017-12-28 forwards_paper.tex
update pseudo-methods

Any simulation scheme that records data into tables,
as does Algorithm~\algref{W},
has its genealogical history available at any time as a tree sequence.
This has two additional advantages:
First, simplification can be run periodically through the simulation,
if we take the set of samples to be the entire currently alive population.
This is important in practice as it keeps memory usage from growing linearly (and quickly) with time.
Second, the simulation can
be \emph{begun} with a tree sequence produced by some other method -- for
instance, by a coalescent simulation with \msprime,
providing an easy, efficient way to specify prior history.
A natural question is now: how often should simplification occur?
As shown in the next section,
there is no computational advantage to simplifying more often than is necessary
to keep memory usage down.

\krt{Empirically, I did find that simplifying more often than every 1,000 generations gave a run-time hit of about 25
percent???}

@@

\begin{enumerate}
    \item \fwdpy{} 0.13.a0
    \item \fwdpp{} 0.5.7
    \item GNU Scientific Library 1.16
    \item pybind11 2.2.1
    \item GCC 4.8.5
\end{enumerate}

All of the above installed via conda.

>>>>

Any simulation scheme that records data into tables,
as does Algorithm~\algref{W},
has its genealogical history available at any time as a tree sequence.
This has two additional advantages:
First, simplification can be run periodically through the simulation,
if we take the set of samples to be the entire currently alive population.
This is important in practice as it keeps memory usage from growing linearly (and quickly) with time.
Second, the simulation can
be \emph{begun} with a tree sequence produced by some other method -- for
instance, by a coalescent simulation with \msprime,
providing an easy, efficient way to specify prior history.
A natural question is now: how often should simplification occur?  We did some limited testing with the C++
implementation of our simulations, and found that different simplification intervals affect run times by approximately
25\%, with the lowest run time occuring when simplifying every $10^3$ generations.  Thus, there is a memory-versus-speed
tradeoff as simplifying more often would keep fewer extinct nodes and edges in memory.  The run-time costs associated
with simplifying have to do with preparing the data to be sent to the simplification algorithm, rather than with the
algorithm itself, which we show in the next section has linear time complexity.

% As shown in the next section,
% there is no computational advantage to simplifying more often than is necessary
% to keep memory usage down.
% 
% \krt{Empirically, I did find that simplifying more often than every 1,000 generations gave a run-time hit of about 25
% percent???}

@@

\begin{enumerate}
    \item \fwdpy{} 0.13.a0
    \item \fwdpp{} 0.5.7
    \item GNU Scientific Library 1.16
    \item pybind11 2.2.1
    \item GCC 4.8.5
    \item msprime master branch
\end{enumerate}

All of the above installed via conda, except for msprime, which must be installed from GitHub.
